---
title: "Homework 1"
author: "Murrel Pereira"
date: "9/19/2020"
output: html_document

---
This is my solution to HW1

```{r echo=FALSE}
library(tidyverse)
```

## Problem 1

Create a dataframe with the specified elements

```{r create_df}
prob1_df = 
tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a", "b", "c", "d","e","f","g","h","i","j"),
  factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)
```

Take the mean of each variable in my data frame

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))

```

I can take the mean of numbers and logical but not characters or factor

```{r echo=FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))

```



```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```
We cannot use these for the factors

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

The penguins dataset is a compilation of observations of penguin species (`r paste(levels(penguins$species), collapse = ", ")`) on the islands of `r paste(levels(penguins$island), collapse = ", ")` from `r min(penguins$year)` - `r max(penguins$year)`. Bill length, bill depth, flipper length, body mass, and sex were variables that were captured.

